### 2014-03-17 src/analysis.Rnw
Updates from amin, fix for graph

\begin{table*}
\begin{minipage}[htb]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results. (left: Original, right: Generated)}
\label{tbl:xselsample}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.round), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.round), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The round(x)\% random selection criteria results. (left: Original, right: Generated)}
\label{tbl:xselround}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.ceil), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.ceil), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The ceil(x)\% random selection criteria results. (left: Original, right: Generated)}
\label{tbl:xselceil}
\end{table*}

@@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\caption {The line count selection criteria results. (left: Original, right: Generated)}
\label{tbl:lcountl}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc.w), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc.w), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\caption {The line count selection criteria results (within). (left: Original, right: Generated)}
\label{tbl:lcountw}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results. (left: Original, right: Generated)}
\label{tbl:onesel}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xop), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xop), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {The x\% per operator criteria results. (left: Original, right: Generated)}
\label{tbl:onesel}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {Operators (left: Original, right: Generated)}
\label{tbl:operators}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\bigskip
\caption {Operator Selection (left: Original, right: Generated)}
\label{tbl:opsel}
\end{table*}

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
o.xp.sample$type <- factor(o.xp.sample$type, levels=c('project','class','method','line'))
ggplot(subset(o.xp.sample, reduction < 100), aes(factor(power), reduction, fill=type, dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + #facet_wrap(~type) +
  myopts +
  #xlab(label=expression(frac(all,sample))) +
  xlab(label=expression(all%/%sample)) +
  ylab('reduction') +
  #theme(legend.position="none") +
  opts(title="sample(x)")
# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
# 
# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
# 
# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
# 
# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Original set $R^2 > 0.90$. Notice the hierarchy of spread within boxplot for similar sampling ratios ($\div$) project < class < method < line i.e project is better}
\label{fig:powerplot}
\end{figure*}

@@

\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=

>>>>

\begin{table*}[!ht]
\begin{minipage}[h]{0.49\linewidth}
\caption*{Original}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
\caption*{Generated}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
%\medskip
\caption {The sample(x)\% random selection criteria results. }
\label{tbl:xselsample}
\end{table*}

\begin{table*}[!ht]
\begin{minipage}[h]{0.49\linewidth}
\caption*{Original}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.round), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
\caption*{Generated}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.round), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
%\medskip
\caption {The round(x)\% random selection criteria results. }
\label{tbl:xselround}
\end{table*}

\begin{table*}[!ht]
\begin{minipage}[h]{0.49\linewidth}
\caption*{Original}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.ceil), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
\caption*{Generated}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.ceil), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
%\medskip
\caption {The ceil(x)\% random selection criteria results. }
\label{tbl:xselceil}
\end{table*}

@@

\begin{table*}[!ht]
\begin{minipage}[h]{0.49\linewidth}
\caption*{Original}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
\caption*{Generated}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
%\medskip
\caption {The line count selection criteria results. }
\label{tbl:lcountl}
\end{table*}

\begin{table*}[!ht]
\begin{minipage}[h]{0.49\linewidth}
\caption*{Original}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc.w), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
\caption*{Generated}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc.w), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
%\medskip
\caption {The line count selection criteria results (within). }
\label{tbl:lcountw}
\end{table*}

\begin{table*}[!ht]
\begin{minipage}[h]{0.49\linewidth}
\caption*{Original}
<<results='asis'>>=
print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
\caption*{Generated}
<<results='asis'>>=
print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
%\medskip
\caption {The one per element selection criteria results. }
\label{tbl:onesel}
\end{table*}

\begin{table*}[!ht]
\begin{minipage}[h]{0.49\linewidth}
\caption*{Original}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xop), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
\caption*{Generated}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xop), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
%\medskip
\caption {The x\% per operator criteria results. }
\label{tbl:onesel}
\end{table*}

\begin{table*}[!ht]
\begin{minipage}[h]{0.49\linewidth}
\caption*{Original}
<<results='asis'>>=
print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
\caption*{Generated}
<<results='asis'>>=
print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
%\medskip
\caption {Operators}
\label{tbl:operators}
\end{table*}

\begin{table*}[!ht]
\begin{minipage}[h]{0.49\linewidth}
\caption*{Original}
<<results='asis'>>=
print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
\caption*{Generated}
<<results='asis'>>=
print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small',sanitize.text.function=function(x){x})
@
\end{minipage}
%\medskip
\caption {Operator Selection}
\label{tbl:opsel}
\end{table*}

\begin{figure*}[htb]
<<x.per.sel.sample,fig.width=10, fig.height=8, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
o.xp.sample$type <- factor(o.xp.sample$type, levels=c('project','class','method','line'))
ggplot(subset(o.xp.sample, reduction < 100), aes(factor(power), reduction, fill=type, dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + #facet_wrap(~type) +
  myopts +
  #xlab(label=expression(frac(all,sample))) +
  xlab(label=expression(sample%/%all)) +
  ylab('reduction') +
  #theme(legend.position="none") +
  opts(title="sample(x)") +
  scale_x_discrete(breaks=c(1,2,3,4,5,6), labels=c("1/2", "1/4", "1/8",'1/16','1/32','1/64'))
# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
# 
# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
# 
# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
# 
# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Original set $R^2 > 0.90$. Notice the hierarchy of spread within boxplot for similar sampling ratios ($\div$) project < class < method < line i.e. project is better}
\label{fig:powerplot}
\end{figure*}

@@

\begin{figure*}[htb]
<<op.all,fig.width=10, fig.height=8, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=

### 2014-03-17 src/methodology.Rnw
Updates from amin, fix for graph

\subsection{Operator Selection}

For selective methods, we tried mutation operators
suggested by Wong et al.~\cite{wong1995reducing}, Offutt et
al.~\cite{offutt1996anexperimental,deng2013empirical}, and, Namin et
al.~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized
operator selection mechanisms, we also compared the Javalanche operators for
operator selection. Note that all of these techniques except Javalanche have
targeted C programs. Thus, some of these operators are sensible in C but not
in Java programs. For example, deletion of return statement is tolerated in C,
not in Java.  Moreover, there were a few operators that were not supported
by the PIT, and could not be implemented easily (as mentioned below).

\subsubsection{Criteria I} For this criteria, we used the two operators
\pitcb and \pitnc which are similar to those given by Wong. We did not have
ABS operator available in PIT.

\subsubsection{Criteria II} We used the operators given by Offutt et
al. \Pitin, \Pitm, \Pitcb, \Pitnc. We did not have LCR available in PIT.

\subsubsection{Criteria III} Those given by Javalanche : \Pitnc, \Pitvmc,
\Pitnvmc, \Pitm, \Pitic, \Pitemv.

\subsubsection{Criteria IV} Given by Namin et
al~\cite{siami2008sufficient}. Many of these operators were not applicable
in Java, and some not in PIT. The operators used by us were \Pitin, \Pitm,
\Piti, \Pitnc.

\subsubsection{Criteria V} In this criteria suggested by
Offutt et al.~\cite{offutt1993experimental} the most numerous operators are
discarded at each step. Our order was:
\Pitnvmc, \Pitnc, \Pitrc, \Pitdc, \Pitrv, \Pitic, \Pitcc, \Pitemv, \Pitvmc,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, \Pitin.

\subsubsection{Statement Deletion:} \label{subsec:stmtdel} The basic
statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements were
modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri~for
simple statements, and using \pitrc for control structures. \pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.  Finally, to get an accurate estimation
of the effect of true statement deletion, we grouped the mutants by
line, and considered each line a single virtual mutant (that is, the total
number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the
virtual statement deletion operator.  We note that the approximation
of simple statement deletion, especially when arithmetic operators are
involved, is not complete. However, as seen in Figure~\ref{fig:op},
the number of mutants produced by \pitm operator is very small. We
also note that our approximation does not account for the increase in
ease of detection when multiple mutations are combined together due to
the coupling effect. This also means that not all the lines may be
mutated ,since there may be no applicable operators. However, given
the constraints of a bytecode based mutation system, we believe that
our procedure is reasonable.
% An interesting point is that using this
%procedure statement, deletion is no longer a simple mutation and
%qualifies as a higher order mutation operator. In fact, the procedure
%we outlined can be used in general to judge the effectiveness of a
%higher order operator from the results of the first order mutation
%operators that together compose the higher order mutant.

>>>>

\subsection{Operator Selection}
For selective methods, we tried mutation operators
suggested by Wong et al.~\cite{wong1995reducing}, Offutt et
al.~\cite{offutt1996anexperimental,deng2013empirical}, and, Namin et
al.~\cite{siami2008sufficient}. Since Javalanche~\cite{javalanche} utilized
operator selection mechanisms, we also compared the Javalanche operators for
operator selection. Note that all of these techniques except Javalanche have
targeted C programs. Thus, some of these operators may be sensible in C but not
in Java. For example, deletion of return statement is tolerated in C,
not in Java.  Moreover, there were a few operators that were not supported
by the PIT, and could not be implemented easily (as mentioned below).

\subsubsection{Constrained Mutation}
\noindent\textbf{Wong et al. ~\cite{wong1995reducing}.}
They selected ROR  and ABS  from Mothra for
mutation analysis. We used operators
\pitcb and \pitnc to model ROR operator. There are no comparable operators to ABS in PIT.

\subsubsection{E-Selective}
\noindent\textbf{Offut et al. \cite{offutt1996anexperimental}.}
They selected ABS, UOI, LCR, AOR, ROR from Mothra operators.
We have used  \Pitin, \Pitm, \Pitcb, and \Pitnc. PIT does not have any operator
comparable to LCR.

\subsubsection{Javalanche}
\noindent\textbf{Javalanche \cite{javalanche}.}
Javalanche uses Negate Jump Condition, Omit Method
 Call, Replace Arithmetic Operator, and Replace Numerical
 Constant operators. We have used \Pitnc, \Pitvmc,
\Pitnvmc, \Pitm, \Pitic and \Pitemv to model them.

\subsubsection{Variable Reduction}
\noindent\textbf{Namin et al.~\cite{siami2008sufficient}.}
They have tried to reduce the mutation operators of Proteum analysis
tool which is for C programs. They suggest 28 operators which many of them
are not applicable in Java, and some not in PIT.
We  used by  \Pitin, \Pitm, \Piti and \Pitnc.

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
$n$ most numerous operators. In our experiment, the order of operators was
\Pitnvmc, \Pitnc, \Pitrc, \Pitdc, \Pitrv, \Pitic, \Pitcc, \Pitemv, \Pitvmc,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin. We discarded one at each
step and evaluated the effectiveness at each $n$.
%----------------------------------------
\subsubsection{Statement Deletion:} \label{subsec:stmtdel} The basic
statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements were
modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri~for
simple statements, and using \pitrc for control structures. \pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.  Finally, to get an accurate estimation
of the effect of true statement deletion, we grouped the mutants by
line, and considered each line a single virtual mutant (that is, the total
number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the
virtual statement deletion operator.  We note that the approximation
of simple statement deletion, especially when arithmetic operators are
involved, is not complete. However, as seen in Figure~\ref{fig:op},
the number of mutants produced by \pitm operator is very small. We
also note that our approximation does not account for the increase in
ease of detection when multiple mutations are combined together due to
the coupling effect. This also means that not all the lines may be
mutated ,since there may be no applicable operators. However, given
the constraints of a bytecode based mutation system, we believe that
our procedure is reasonable.
% An interesting point is that using this
%procedure statement, deletion is no longer a simple mutation and
%qualifies as a higher order mutation operator. In fact, the procedure
%we outlined can be used in general to judge the effectiveness of a
%higher order operator from the results of the first order mutation
%operators that together compose the higher order mutant.

### 2014-03-17 src/paper.Rnw
Updates from amin, fix for graph

#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
<<>>=
theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())

>>>>

#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(scales)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
<<>>=
theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())
